Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-22 bdcloud_paper/latex/paper.tex
Added relational data model

\textcolor{red}{relational data model diagram?}

\subsection{Stores}

@@

\subsection{Customers}

Customer records consist of a unique identifier, a name, a location given as a 5-digit zip code, and the number and species of their pets.

@@

\subsection{Transactions}
A transaction model is created for each customer and integrated over the simulation's time frame to generate transactions. Transaction records consist of a customer, a store, a date and time, and a list of items purchased and their prices.  The store is set to the store located closest to the customer. The date and time is given as a floating-point number with units of days since the start of the simulation.  (Time zones are not taken into account.)  Transaction times are generated from a Monte Carlo process based on the customer will use up items such as dog food (Section~\ref{sec:transaction-times}).  The purchased items are generated by a Hidden Markov Model (HMM) parameterized by the transaction time and amount of time remaining for the items in the customer's inventory (Section~\ref{sec:transaction-purchases}).

@@

\subsubsection{Transaction Times} \label{sec:transaction-times}

>>>>

\subsection{Relational Data Model}
The model generates data for four types of records: stores, customers, transactions, and transaction items (Figure~\ref{fig:relational-data-model}).  Store records contain both a unique identifier and a location in the form of a 5-digit zip code. Customer records consist of a unique identifier, a name, and a location given as a 5-digit zip code. Transaction records consist of a customer identifier, a store identifier, and a time. Transaction item records contain a transaction identifier and an item description.  The item description is a list of key-value pairs stored as a string.  Key-value pairs are used since item characteristics differ depending on the type of item.  For example, dog food has a brand, a flavor, a size (in lbs), and a per-unit cost, while poop bags have a brand, a color, a count, and a per-unit cost.

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.5in]{figures/transactions_data_model.eps}
  \caption{Relational Data Model for Generated Data}
  \label{fig:relational-data-model}
\end{figure}

\subsection{Generation of Stores}

@@

\subsection{Generation of Customers}
Customer records consist of a unique identifier, a name, a location given as a 5-digit zip code, and the number and species of their pets.

@@

\subsection{Simulation of Transactions}
A transaction model is created for each customer and integrated over the simulation's time frame to generate transactions. Transaction records consist of a customer, a store, a date and time, and a list of items purchased and their prices.  The store is set to the store located closest to the customer. The date and time is given as a floating-point number with units of days since the start of the simulation.  (Time zones are not taken into account.)  Transaction times are generated from a Monte Carlo process based on the customer will use up items such as dog food (Section~\ref{sec:transaction-times}).  The purchased items are generated by a Hidden Markov Model (HMM) parameterized by the transaction time and amount of time remaining for the items in the customer's inventory (Section~\ref{sec:transaction-purchases}).

@@

\subsubsection{Simulation of Transaction Times} \label{sec:transaction-times}
